---
title: "main_basic_preprocessing"
output: html_document
date: "2025-10-09"
---
This is the basic pre-processing for this study--to create a cleaned, anonymized csv for use in the rest of the analyses. Also, to plot basic performance metrics.

The setup was:
4 spatial recall practice
4 digit span practice
4 rest practice

10 blocks, 3 epochs per group
- 10 digit span per epoch
- 10 visual search per epoch
- up to 20 rest trials per rest period

group ordering: ABABBABAAB

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("broom")      # for tidying up linear models 
library("car")        # for running ANOVAs
library("afex")       # also for running ANOVAs
library("emmeans")    # for calculating constrasts
library(jsonlite)

# set the default ggplot theme 
theme_set(theme_classic())
```

**reading in the data**
``` {r vars}
# exp vars
sr_practice_num <- 4
sr_per_block <- 10
ds_practice_num <- 4
ds_per_block <- 10
rt_practice_num <- 4
rt_per__block_max <- 20
num_groups <- 10
num_blocks_per_group <- 3
num_blocks_overall <- num_groups * num_blocks_per_group
```

``` {r read_in_data}
# data from proliferate
setwd("../data/test_run/")
data_file <- list.files(pattern = "\\-merged.csv$")

# Function to read a CSV file and convert all columns to character type
read_csv_as_character <- function(file) {
  df <- read.csv(file, stringsAsFactors = FALSE)
  df[] <- lapply(df, as.character)  # Apply as.character to each column
  return(df)
}

df_all <- read_csv_as_character(data_file)
```

``` {r past_payments}
# LEAVE COMMENTED OUT UNTIL YOU GET MORE PARTICIPANTS THEN RUN THIS ONCE AND COMMENT OUT AGAIN
# read in previous subj_ids that you've already approved/paid so you don't double do it
# setwd("../data/test_run/")
# already_paid <- read.csv("already_paid.txt",header = FALSE,
#                         col.names = "prolific_id",
#                         stringsAsFactors = FALSE)

# get the participant id and bonus for repayment
df_bonus_id <- df_all %>%
  filter(str_detect(tolower(response), "prolific_id") | !is.na(final_bonus)) %>%
  mutate(subj_id = as.numeric(workerid)) %>%
  select(subj_id, response, final_bonus) %>%
  group_by(subj_id) %>%
  summarise(
    prolific_id = first(response[str_detect(response, "prolific_id")]),
    final_bonus = first(final_bonus[!is.na(final_bonus)]),
    .groups = "drop"
  ) %>%
  # extract the prolific_id from the JSON string
  mutate(
    prolific_id = gsub(".*'prolific_id':\\s*'([^']+)'.*", "\\1", prolific_id),
    final_bonus = as.numeric(final_bonus)
  )
```

**pre-processing the data**

Anonymize the data and remove unneccesary columns, also gets rid of prolific id:
``` {r data_wrangling_anonymize}
# anonymize and change worker id to subj_id
anonymize_clean <- function(df) {
  df <- df %>%
    select(-url,-proliferate.condition,-failed_audio, -failed_images, -failed_video,
           -sequence_length,-internal_node_id,-view_history,-contains("browser"),-contains("platform"),
         -contains("screen"),-contains("width"),-contains("height"),
         -contains("failed"),-success,-event_history, -internal_node_id) %>%
    filter(!str_detect(tolower(response), "prolific_id"))%>%
    mutate(subj_id = as.numeric(workerid))
  return(df)
}
df_all <- anonymize_clean(df_all)
```

Basic cleaning and data wrangling of the anonymized data: 
- this removes non game trials (and saves the survey data to a different data frame)
``` {r data_wrangling}
df_all <- df_all %>%
  # IMPORTANTLY: marks timeouts as incorrect
  mutate(is_correct_numeric = ifelse(is_correct=="false" | timed_out == "1" | 
                                       timed_out == "true" | timed_out == 1, 0, 1)) %>%
  group_by(subj_id) %>%
  mutate(
    gameA = ifelse(all(is.na(gameA_name)), NA, 
                   first(gameA_name[!is.na(gameA_name) & !(gameA_name=="")])),
    SR_isGameA = ifelse(all(is.na(gameA_isSR)), NA,
                        first(gameA_isSR[!is.na(gameA_isSR) & !(gameA_isSR == "")]))
  ) %>%
  mutate(gameA_isSR = ifelse(SR_isGameA == "true", TRUE, FALSE), gameA_name = gameA) %>%
  ungroup()

df_recent_subset <- df_all %>%
  filter(trial_type == "sr_practice_response" | trial_type == "ds_practice_response" | trial_type == "rt_practice_trials" | trial_type == "sr_main_response" | trial_type == "ds_main_response" | trial_type == "rt_main_trials") %>%
  select(-c(transition_type, gameB_name, game_A, game_B, backwards, score_an, score_pc, score_ls, is_correct, stimulus, target_shape, final_bonus)) %>%
  ungroup() %>%
  mutate(trial_index_num = as.numeric(trial_index)) %>%
  mutate(trial_index = trial_index_num) %>%
  select(-trial_index_num, -SR_isGameA, -gameA) %>%
  arrange(subj_id, trial_index)
```

Saves the practice runs in a separate dataframe, and also changes is_correct into a true/false, calculates avg performance on each task, gets rid of unnecessary columns
``` {r data_wrangling_avgs}
# create the pratice runs df and save it
practice_runs_subset_df <- df_recent_subset %>%
  filter(trial_type == "sr_practice_response" | trial_type == "ds_practice_response" | trial_type == "rt_practice_trials") %>%
  group_by(subj_id, trial_type) %>%
  summarize(avg_accuracy = mean(is_correct_numeric))
# save the practice data to a cleaned csv
setwd("../data_cleaned/test_run/")
write.csv(practice_runs_subset_df, "practice_trials_cleaned.csv")


# exclude practice runs from the main dataset and create a df with the average performance per worker per task
all_runs_avg_subset <- df_recent_subset %>%
  filter(trial_type == "sr_main_response" | trial_type == "ds_main_response" | trial_type == "rt_main_trials") %>%
  group_by(subj_id, trial_type) %>%
  summarize(avg_accuracy = mean(is_correct_numeric))
```

Add epoch labels to each epoch, and block numbers to each block
Will do: 1,2,3,4,5,6,etc so up to 30 for the epochs
``` {r data_wrangling_blocks_groups}
# make sure it's arranged in order and remove practice rows
df_recent_subset_analyze <- df_recent_subset %>%
  filter(trial_type != "sr_practice_response" & trial_type != "ds_practice_response" & trial_type != "rt_practice_trials") %>%
  arrange(subj_id, trial_index) %>%
  ungroup() %>%
  # add overall trial counts of each task
  group_by(subj_id, game_type) %>%
  arrange(trial_index) %>%
  mutate(overall_type_count = row_number()) %>%
  ungroup() %>%
  # add the epoch numbers and block values
  arrange(subj_id, trial_index) %>%
  group_by(subj_id) %>%
  mutate(
    epoch_num = cumsum(game_type == "rest_task" & lag(game_type, default = first(game_type)) != "rest_task"),
    block_num = ifelse(game_type == "rest_task" & follows_block_num != "null", follows_block_num, NA)
  ) %>%
  fill(block_num, .direction = "up") %>%
  mutate(
    epoch_num = ifelse(is.na(epoch_num), 1, epoch_num)
  ) %>%
  ungroup() %>%
  # reset the epoch numbers to start from 1 for each participant
  # get rid of epoch num for rest task
  group_by(subj_id) %>%
  mutate(
    epoch_num = ifelse(epoch_num >= 0, dense_rank(epoch_num), epoch_num),
    epoch_num = ifelse(game_type == "rest_task", NA, epoch_num)
  ) %>%
  select(-option_to_end, -overall_num_rest_used, -end_rest_button_clicked, -responses, -timeout) %>%
  ungroup() %>%
  arrange(subj_id, trial_index)
```


``` {r data_wrangling_blocks_groups}
df_recent_subset_analyze <- df_recent_subset_analyze %>%
  mutate(na_trial = ifelse(is.na(timed_out), 1,0),
        timed_out = ifelse(timed_out == "true" | timed_out == 1 | timed_out == "1", TRUE, FALSE)) %>%
  mutate(rt = ifelse(timed_out == TRUE,NA,rt)) %>% # for all tasks, if timed out rt = 4200 or 5000 ms; for SR sometimes it's slightly above 4200 if it didn't catch it in time
  mutate(rt_num = as.numeric(rt)) %>%
  mutate(rt = rt_num) %>%
  select(-rt_num)

# count rests taken per break (label rest chunk per participant (should be 30) and add a column which counts how many per break there are)
df_recent_subset_analyze <- df_recent_subset_analyze %>%
  ungroup() %>%
  arrange(subj_id, trial_index) %>%
  group_by(subj_id) %>%
  mutate(task_change = game_type != lag(game_type, default = "first_row"),
         rest_chunk = cumsum(task_change & game_type == "rest_task"),
         rest_chunk = ifelse(game_type == "rest_task", rest_chunk, NA)) %>%
  ungroup() %>%
  group_by(subj_id, rest_chunk) %>%
  mutate(num_rest_in_chunk = sum(!is.na(rest_chunk))) %>%
  select(-task_change) %>%
  ungroup()

# save the cleaned subset data
setwd("../data_cleaned/test_run/")
write.csv(df_recent_subset_analyze, "main_trials_cleaned.csv")
```


``` {r data_wrangling_timeouts}
# count how much each participant timed out (to make sure no participants exited the task early and that none of them just let the task play out without participating)
prop_timed_out <- df_recent_subset_analyze %>%
  ungroup() %>%
  group_by(subj_id, game_type) %>%
  summarize(num_timed_out = sum(timed_out == TRUE), num_not_timed_out = sum(timed_out == FALSE), num_NA = sum(na_trial == 1)) %>%
  mutate(total_trials = num_not_timed_out + num_timed_out,
         prop_timed_out = num_timed_out / total_trials)

# save time out counts to the subj_id / bonus table 
final_participant_data <- df_bonus_id %>%
  left_join(prop_timed_out, by = "subj_id") 

final_participant_data <- final_participant_data%>%
  group_by(subj_id) %>%
  mutate(max_timed_out_sr_ds = max(
        case_when(
          game_type %in% c("spatial_recall", "digit_span") ~ prop_timed_out,
          TRUE ~ NA_real_
        ),na.rm = TRUE))

# bonus stuff used to be here, now its at the bottom of this cell
```
Save survey results:
``` {r data_wrangling_survey}
python_dict_to_json <- function(text) {
  text %>%
    str_replace_all("'", '"') %>%
    str_replace_all("None", "null") %>%
    str_replace_all("True", "true") %>%
    str_replace_all("False", "false")
}

df_separated <- df_separated %>%
  mutate(response = map_chr(response, python_dict_to_json))

# Parse rest survey responses
rest_responses <- df_separated %>%
  filter(survey_type == "rest_survey") %>%
  mutate(
    parsed = map(response, possibly(fromJSON, otherwise = NULL))
  ) %>%
  unnest_wider(parsed) %>%
  select(-response, -survey_type)

# Parse game survey responses
game_responses <- df_separated %>%
  filter(survey_type == "game_survey") %>%
  mutate(
    parsed = map(response, possibly(fromJSON, otherwise = NULL))
  ) %>%
  unnest_wider(parsed) %>%
  select(-response, -survey_type)

# Join them back together
survey_cleaned <- rest_responses %>%
  full_join(game_responses, by = "subj_id", suffix = c("_rest", "_game"))

setwd("../data_cleaned/test_run/")
write.csv(survey_cleaned, "survey_cleaned.csv", row.names = FALSE)
``` 

``` {r data_wrangling_bonus}
# check to see if any participants timed out too much on spatial recall or digit span

# too many timeouts = >85% (if they did, look into their responses to see if they tried to respond)
# also check to see if anyone has <150 trials for ds or sr (means they didn't complete the task for some reason)
df_bonus_id <- final_participant_data %>%
  ungroup() %>%
  mutate(flagged_time_outs = ifelse(max_timed_out_sr_ds > 0.85, TRUE, FALSE),
         flagged_few_trials = ifelse(game_type != "rest_task" & total_trials < 150, TRUE, FALSE),
         flagged_has_nas = ifelse(num_NA != 0, TRUE, FALSE)) # figure out whats happening w 539 subj

# print the ones who you should look into more
df_bonus_id %>%
  filter(flagged_time_outs == TRUE | flagged_few_trials == TRUE | flagged_has_nas == TRUE) %>%
  # filter(!(prolific_id %in% already_paid_1$prolific_id)) %>% #this lets me filter out those I already approved (did everyone in batch 1)
  # filter(!(prolific_id %in% already_paid_2$prolific_id)) %>% #this lets me filter out those I already approved/looked at
  print() %>%
  select(subj_id, prolific_id, flagged_time_outs, max_timed_out_sr_ds, flagged_few_trials, flagged_has_nas) %>%
  distinct()


# filter out/exclude those who have more than 85% na trials (for sr or ds)
exclude_has_nas <- df_bonus_id%>%
  filter(flagged_has_nas == TRUE) %>%
  select(subj_id)

exclude_has_nas

```

``` {r data_wrangling_bonus}
# save the timed out data which you can save in the anonymous folder
prop_timed_out <- df_bonus_id %>%
  # filter(!(subj_id %in% exclude_has_nas)) %>% # exclude for now
  select(-prolific_id, -final_bonus, -max_timed_out_sr_ds)

setwd("../data_cleaned/test_run/")
write.csv(prop_timed_out, "timed_out_data_cleaned.csv")

```


``` {r data_wrangling_bonus}
# clean the bonus_id df which you will then use for paying bonuses (DO NOT UPLOAD THIS FILE TO data_anonymized FOLDER) but can update to data/ because it's hidden with gitignore (can then upload this to prolific for an easy way to pay bonuses)

setwd("../data/test_run/")
# for batch 1
subj_to_exclude =  exclude_has_nas$subj_id #excluding the ones with incomplete data
df_bonus_id_b1 <- df_bonus_id %>%
  select(subj_id, prolific_id, final_bonus) %>%
  distinct() %>%
  # filter(!(subj_id %in% subj_to_exclude)) %>%
  # filter(!(prolific_id %in% already_paid_1$prolific_id)) %>% #this lets me filter out those I already approved/looked at
  select(prolific_id, final_bonus)
write.table(df_bonus_id_b1, "bonus_payments.txt", sep=",", row.names=FALSE, col.names=FALSE, quote=FALSE)
# find certain prolific ids here
# df_bonus_id %>%
#   filter(prolific_id %in% c(""))

df_bonus_id <- df_bonus_id %>%
  select(-prolific_id)
df_bonus_id_b1 <- df_bonus_id_b1 %>%
  select(-prolific_id)
```

## Basic Plots and Checks:

Plot average accuracies per task per person:
``` {r avg_acc_pre_exclusion}
all_runs_avg_subset %>%
  ggplot(aes(x=trial_type,y=avg_accuracy,color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  # facet_wrap(~trial_type)+
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game types",y="Average accuracy per participant on given game type")+
  ggtitle("Average participant performance on each game: pre-exclusion")

```


Plot average RT per task per person:
``` {r avg_rt_pre_exclusion}
rt_overall_avgs <- df_recent_subset_analyze %>%
  ungroup() %>%
  filter(timed_out == FALSE) %>%
  group_by(subj_id, game_type) %>%
  summarize(rt_avg = mean(rt))

rt_overall_avgs %>%
  ggplot(aes(x=game_type,y=rt_avg,color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  # facet_wrap(~trial_type)+
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game types",y="Average rt per participant on given game type")+
  ggtitle("Average participant rt on each game: pre-exclusion")



df_recent_subset_analyze <- df_recent_subset_analyze %>%
  select(-correct_response, -rest_trial_num, -end_rest)
```


Plot performance over time SR and DS and Rest Task per person:
``` {r perf_over_time_pre_exclusion}
avg_accuracy_blocks <- df_recent_subset_analyze %>%
  ungroup() %>%
  group_by(subj_id, block_num, group_num, game_type) %>%
  summarise(avg_accuracy = mean(is_correct_numeric))

avg_accuracy_blocks %>%
  filter(game_type == "spatial_recall") %>%
  ggplot(mapping = aes(x=block_num, y=avg_accuracy, color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  geom_smooth(method = "lm", se = TRUE) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  ylim(0,1) +
  # stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Block number",y="Average accuracy per participant in given block")+
  ggtitle("Spatial recall: Average accuracy over time: pre-exclusion")



avg_accuracy_blocks %>%
  filter(game_type == "digit_span") %>%
  ggplot(mapping = aes(x=block_num, y=avg_accuracy, color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  geom_smooth(method = "lm", se = TRUE) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  ylim(0,1) +
  # stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Block number",y="Average accuracy per participant in given block")+
  ggtitle("Digit span: Average accuracy over time: pre-exclusion")



avg_accuracy_blocks %>%
  filter(game_type == "rest_task") %>%
  mutate(group_num = as.numeric(group_num)) %>%
  ggplot(mapping = aes(x=group_num, y=avg_accuracy, color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  geom_smooth(method = "lm", se = TRUE,formula = y ~ x) +
  ylim(0,1) +
  # stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Group number",y="Average accuracy per participant in given group")+
  ggtitle("Rest task: Average accuracy over time: pre-exclusion")

```

Plot rests taken over time:
``` {r rests_over_time_pre_exclusion}
df_recent_subset_analyze %>%
  filter(game_type == "rest_task") %>%
  select(subj_id, rest_chunk, num_rest_in_chunk) %>%
  group_by(subj_id, rest_chunk, num_rest_in_chunk) %>%
  distinct() %>%
  ungroup() %>%
  ggplot(mapping = aes(x=rest_chunk, y=num_rest_in_chunk, color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  geom_smooth(method = "lm", se = TRUE,formula = y ~ x) +
  labs(x="Rest period number",y="Number of rests taken")+
  ggtitle("Average number of rests taken over time: pre-exclusion")
  
```


Plot average proportion of timeouts per task:
``` {r rests_over_time_pre_exclusion}
df_recent_subset_analyze %>%
  ungroup() %>%
  group_by(subj_id, game_type) %>%
  summarize(num_timed_out = sum(timed_out == TRUE), num_not_timed_out = sum(timed_out == FALSE)) %>%
  mutate(total_trials = num_not_timed_out + num_timed_out,
         prop_timed_out = num_timed_out / total_trials) %>%
  ggplot(mapping = aes(x=game_type, y=prop_timed_out, color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  labs(x="Game type",y="Proportion of trials timed out")+
  ggtitle("Proportion of trials timed out, per game type: pre-exclusion")
```

# DO EXCLUSION CRITERIA:
- excluding participants based on:
1. accuracy below 30% on both tasks (digit span and spatial recall) (signifying a lack of attention/trying) or above 95% on both tasks
2. those with incomplete data (had some glithc; only one; saved in: exclude_has_nas)

``` {r pre_exclusion_plots}
# average of all subj averages
all_runs_avg_subset %>%
  ggplot(mapping = aes(x=trial_type,y=avg_accuracy, color=subj_id)) +
 geom_point(alpha = 0.3,position = position_jitter(width = 0.4,
                              height = 0.01)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game Type",y="Average accuracy on all trials, per subject", title = "Average of subject mean performance on each game (pre-exclusion)",size = 30) +
  theme(text = element_text(size = 13))


# median of subject averages
all_runs_avg_subset %>%
 ggplot(mapping = aes(x=trial_type,y=avg_accuracy, color=subj_id)) +
 geom_point(alpha = 0.3,position = position_jitter(width = 0.4,
                              height = 0.01)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = median, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game Type",y="Average accuracy on all trials, per subject", title = "Median of subject mean performance on each game (pre-exclusion)", size = 30) +
  theme(
    text = element_text(size = 12),        # Base text size
    axis.title = element_text(size = 13),  # Axis titles
    axis.text = element_text(size = 13),   # Axis labels
    plot.title = element_text(size = 13)   # Plot title
  )
```
``` {r exclusion}
# cutoffs
top_cutoff = 0.95 # right now, to be cut out must get above this on both tasks
bottom_cutoff = 0.30 # right now, to be cut out must get below this on both tasks

# get subjects above the cutoff on both tasks
subjects_high_low_accuracy <- all_runs_avg_subset %>%
  group_by(subj_id) %>%
  summarize(min_avg_score = min(avg_accuracy), max_avg_score = max(avg_accuracy)) %>%
  filter(min_avg_score > top_cutoff | max_avg_score < bottom_cutoff) %>%
  print()

# DO OTHER EXCLUSION HERE
# remove these subjects from final datasets
all_runs_avg_subset <-  all_runs_avg_subset%>%
  filter(!(subj_id %in% subjects_high_low_accuracy$subj_id),
         !(subj_id %in% exclude_has_nas$subj_id))
survey_cleaned <- survey_cleaned %>%
  filter(!(subj_id %in% subjects_high_low_accuracy$subj_id),
         !(subj_id %in% exclude_has_nas$subj_id))
practice_runs_subset_df <- practice_runs_subset_df %>%
  filter(!(subj_id %in% subjects_high_low_accuracy$subj_id),
         !(subj_id %in% exclude_has_nas$subj_id))
df_recent_subset_analyze <- df_recent_subset_analyze %>%
  filter(!(subj_id %in% subjects_high_low_accuracy$subj_id),
         !(subj_id %in% exclude_has_nas$subj_id))

write.csv(survey_cleaned, "/Users/nastasiaklevak/Desktop/FYP_2024/CognitiveFatigue_TaskSpecificity/data_anonymized/SPRmain/excluded/SPRmain_survey_cleaned.csv")
write.csv(practice_runs_subset_df, "/Users/nastasiaklevak/Desktop/FYP_2024/CognitiveFatigue_TaskSpecificity/data_anonymized/SPRmain/excluded/SPRmain_practice_trials_cleaned.csv")
write.csv(df_recent_subset_analyze, "/Users/nastasiaklevak/Desktop/FYP_2024/CognitiveFatigue_TaskSpecificity/data_anonymized/SPRmain/excluded/SPRmain_main_trials_cleaned.csv")
```


``` {r post_exclusion_plots}
# average of all subj averages
all_runs_avg_subset %>%
  ggplot(mapping = aes(x=trial_type,y=avg_accuracy, color=subj_id)) +
 geom_point(alpha = 0.3,position = position_jitter(width = 0.4,
                              height = 0.01)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game Type",y="Average accuracy on all trials, per subject", title = "Average of subject mean performance on each game (post-exclusion)",size = 30) +
  theme(text = element_text(size = 13))


# median of subject averages
all_runs_avg_subset %>%
 ggplot(mapping = aes(x=trial_type,y=avg_accuracy, color=subj_id)) +
 geom_point(alpha = 0.3,position = position_jitter(width = 0.4,
                              height = 0.01)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = median, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game Type",y="Average accuracy on all trials, per subject", title = "Median of subject mean performance on each game (post-exclusion)", size = 30) +
  theme(
    text = element_text(size = 12),        # Base text size
    axis.title = element_text(size = 13),  # Axis titles
    axis.text = element_text(size = 13),   # Axis labels
    plot.title = element_text(size = 13)   # Plot title
  )
```
``` {r rests_over_time_post_exclusion}
df_recent_subset_analyze %>%
  filter(game_type == "rest_task") %>%
  select(subj_id, rest_chunk, num_rest_in_chunk) %>%
  group_by(subj_id, rest_chunk, num_rest_in_chunk) %>%
  distinct() %>%
  ungroup() %>%
  ggplot(mapping = aes(x=rest_chunk, y=num_rest_in_chunk, color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  geom_smooth(method = "lm", se = TRUE,formula = y ~ x) +
  labs(x="Rest period number",y="Number of rests taken")+
  ggtitle("Average number of rests taken over time: post-exclusion")




rt_overall_avgs <- df_recent_subset_analyze %>%
  ungroup() %>%
  filter(timed_out == FALSE) %>%
  group_by(subj_id, game_type) %>%
  summarize(rt_avg = mean(rt))

rt_overall_avgs %>%
  ggplot(aes(x=game_type,y=rt_avg,color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  # facet_wrap(~trial_type)+
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game types",y="Average rt per participant on given game type")+
  ggtitle("Average participant rt on each game: post-exclusion")
  
```

``` {r prop_skipped_post_exclusion}
df_recent_subset_analyze %>%
  ungroup() %>%
  group_by(subj_id, game_type) %>%
  summarize(num_timed_out = sum(timed_out == TRUE), num_not_timed_out = sum(timed_out == FALSE)) %>%
  mutate(total_trials = num_not_timed_out + num_timed_out,
         prop_timed_out = num_timed_out / total_trials) %>%
  ggplot(mapping = aes(x=game_type, y=prop_timed_out, color=subj_id)) +
  geom_point(alpha = 0.5,position = position_jitter(width = 0.2,
                                        height = 0)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game type",y="Proportion of trials timed out")+
  ggtitle("Proportion of trials timed out, per game type: post-exclusion")

```

IN THE END: excluded 6 so far (1 for incomplete data, 5 for the accuracy exclusion criteria)



# Plot same performance graphs but separate out time out trials:


``` {r post_exclusion_plots}
all_runs_avg_subset_filtered <- df_recent_subset_analyze %>%
  ungroup() %>%
  filter(timed_out == FALSE) %>%
  group_by(subj_id, trial_type) %>%
  summarize(avg_acc_no_timeout = mean(is_correct_numeric))
  

# average of all subj averages (excluding timed out trials)
all_runs_avg_subset_filtered %>%
  ggplot(mapping = aes(x=trial_type,y=avg_acc_no_timeout, color=subj_id)) +
 geom_point(alpha = 0.3,position = position_jitter(width = 0.4,
                              height = 0.01)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = mean, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game Type",y="Average accuracy on all trials, per subject",size = 30) +
  ggtitle("Average of subject mean performance on each game (post-exclusion)", "excluding time out trials")
  theme(text = element_text(size = 13))


# median of subject averages
all_runs_avg_subset_filtered %>%
 ggplot(mapping = aes(x=trial_type,y=avg_acc_no_timeout, color=subj_id)) +
 geom_point(alpha = 0.3,position = position_jitter(width = 0.4,
                              height = 0.01)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "yellow",
               shape = 21,
               size = 1)+
  stat_summary(fun.y = median, geom = "text", aes(label = round(..y.., 2)), hjust = -.5) +
  labs(x="Game Type",y="Average accuracy on all trials, per subject", size = 30) +
  ggtitle("Median of subject mean performance on each game (post-exclusion)","excluding time out trials")
  theme(
    text = element_text(size = 12),        # Base text size
    axis.title = element_text(size = 13),  # Axis titles
    axis.text = element_text(size = 13),   # Axis labels
    plot.title = element_text(size = 13)   # Plot title
  )
```
