---
title: "q1_q3_analysis_graphs"
output: html_document
date: "2025-01-20"
---

Do the same analysis from basic_modeling but make it cleaner and simpler; get graphs for 1 and 3 here (impact of cue_type and previous block accuracy on rest_length)

POST EXCLUSION: should be 84

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("broom")      # for tidying up linear models 
library("car")        # for running ANOVAs
library("afex")       # also for running ANOVAs
library("emmeans")    # for calculating constrasts
library(jsonlite)
library(MASS, exclude = "select")
library(performance)
library(DHARMa)
library(effects)
library(rstatix, exclude="filter")  # For statistical tests
library(ggpubr)
library(patchwork)  # For combining plots
library(report)


# set the default ggplot theme 
theme_set(theme_classic())
```


# READ IN DATA (these are all post-exclusion files from both batches)
``` {r data_loading}
# exp vars
sr_practice_num <- 4
sr_per_block <- 10
ds_practice_num <- 4
ds_per_block <- 10
rt_practice_num <- 4
rt_per__block_max <- 20
num_groups <- 10
num_blocks_per_group <- 3
num_blocks_overall <- num_groups * num_blocks_per_group

df_all <- read.csv("/Users/nastasiaklevak/Desktop/FYP_2024/CognitiveFatigue_TaskSpecificity/data_anonymized/SPRmain/excluded/SPRmain_main_trials_cleaned.csv",stringsAsFactors = FALSE) %>%
  select(-X)
df_practice <- read.csv("/Users/nastasiaklevak/Desktop/FYP_2024/CognitiveFatigue_TaskSpecificity/data_anonymized/SPRmain/excluded/SPRmain_practice_trials_cleaned.csv",stringsAsFactors = FALSE)%>%
  select(-X)
df_survey <- read.csv("/Users/nastasiaklevak/Desktop/FYP_2024/CognitiveFatigue_TaskSpecificity/data_anonymized/SPRmain/excluded/SPRmain_survey_cleaned.csv", stringsAsFactors = FALSE)%>%
  select(-X)
```

# QUESTIONS:
1) Is there a post-error increase in fatigue? i.e. is accuracy a significant negative estimator for subsequent rest time?
3) Is task switching acted upon as rejuvenating? i.e. will rest time when cued that the next block will be a switch be less than when cued the next block will be a stay

# MODELS
Keeping it simple; looking specifically at the effect of avg_block_accuracy and cue_type on the following rests per chunk; looking to see what breaks the effect as we make it more complicated (but don't add an unnecessary number of predictors and overfit)

``` {r data_loading}
# get average per block per subject
rest_info <- df_all %>%
  group_by(subj_id) %>%
  filter(!is.na(rest_chunk), !is.na(type_desc)) %>%
  select(subj_id, block_num = rest_chunk, num_rest_in_chunk, rest_type = type_desc) %>%
  distinct() %>%
  ungroup() %>%
  group_by(subj_id,block_num) %>%
  slice(1)  # Take only the first row for each block

# Then join with summary
df_all_blockwise <- df_all %>%
  ungroup() %>%
  filter(trial_type != "rt_main_trials") %>%
  group_by(subj_id, block_num) %>%
  summarize(
    avg_block_accuracy = mean(is_correct_numeric),
    accuracy_sd = sd(is_correct_numeric),
    avg_rt = mean(rt[!timed_out]),
    rt_sd = sd(rt[!timed_out]),
    group_num = first(group_num),
    gameA_isSR = first(gameA_isSR),
    game_type = first(game_type),
    .groups = 'drop'
  ) %>%
  left_join(rest_info, by = c("subj_id","block_num"))%>%
  mutate(cue_type = ifelse(rest_type == "block_same_same" | rest_type == "group_A_A" | rest_type == "group_B_B", "stay", "switch"))

df_all_blockwise <- df_all_blockwise %>%
  ungroup() %>%
  group_by(subj_id) %>%
  mutate(scale_rest = as.vector(scale(num_rest_in_chunk, center = TRUE, scale = TRUE)),
         scale_accuracy = as.vector(scale(avg_block_accuracy, center = TRUE, scale = TRUE))) %>%
  ungroup()

# just a check to make sure it has all non-excluded participants (84)
df_all_blockwise %>%
  select(subj_id) %>%
  distinct()
```

Simple focused models:
``` {r simple_models}
model_data <- df_all_blockwise

# SIMPLE REST AND CUE MODELS (see what breaks the model)

# avg block accuracy is a significant negative predictor of following rest
fit.rest_basic_model <- glm(num_rest_in_chunk ~ avg_block_accuracy,
                           data = model_data,
                           family = poisson) 
summary(fit.rest_basic_model)

# avg block accuracy is still a negative predictor but insignificant when accounting for subj as mixed effect
fit.rest_basic_model_mixed <- glmer(num_rest_in_chunk ~ avg_block_accuracy + (1|subj_id),
                           data = model_data,
                           family = poisson) 
summary(fit.rest_basic_model_mixed)


# cue type not significant in a glm
fit.cue_basic_model <- glm(num_rest_in_chunk ~ cue_type,
                           data = model_data,
                           family = poisson) 
summary(fit.cue_basic_model)

# cue type not significant on its own
fit.cue_basic_model_mixed <- glmer(num_rest_in_chunk ~ cue_type + (1|subj_id),
                           data = model_data,
                           family = poisson) 
summary(fit.cue_basic_model_mixed)
``` 


Now build up to see when you add other important predictors:
``` {r rest_cue_mixed_models}
# cue type marginally sig.
fit.mixed_1 <- glmer(num_rest_in_chunk ~ avg_block_accuracy + cue_type + (1|subj_id),
                           data = model_data,
                           family = poisson) 
summary(fit.mixed_1)

# cue type marginally sig. (switching has negative impact on rests; told you're switching -> less rest)
fit.mixed_2 <- glmer(num_rest_in_chunk ~ avg_block_accuracy + cue_type + gameA_isSR + (1|subj_id),
                           data = model_data,
                           family = poisson) 
summary(fit.mixed_2)

# cue type sig. (switching has positive impact on rests); but avg_block_accuracy:cue_typeswitch has a significant negative predictor (performing well AND told you're switching -> less rest); SO being told you're switching leads to more rest when you're performing more poorly but as you perform better it doesn't lead to more rests as much
fit.mixed_3 <- glmer(num_rest_in_chunk ~ avg_block_accuracy*cue_type + gameA_isSR + (1|subj_id),
                           data = model_data,
                           family = poisson) 
summary(fit.mixed_3)

# same effects as in mixed 3 but also group number is sig negative predictor (as group gets larger they rest less than before)
fit.mixed_4 <- glmer(num_rest_in_chunk ~ group_num + avg_block_accuracy*cue_type + gameA_isSR + (1|subj_id),
                           data = model_data,
                           family = poisson)
summary(fit.mixed_4)

# same as before ^ 
fit.mixed_5 <- glmer(num_rest_in_chunk ~ group_num + avg_block_accuracy*cue_type + gameA_isSR + game_type + (1|subj_id),
                           data = model_data,
                           family = poisson) 
summary(fit.mixed_5) # switch is pos, switch:acc is neg, group_num is neg, game_type:spatial_recall neg predictor

compare_performance(fit.mixed_1, fit.mixed_2, fit.mixed_3, fit.mixed_4, fit.mixed_5) # five is the best


check_model(fit.mixed_5)

# SEEMS LIKE IT HAS OVERDISPERION: trying these models below as negative bionimals
```


Trying plots from above as negative binomials:
``` {r rest_cue_mixed_models_negbin}
# Model 1: avg_block_accuracy is a sig. neg predictor 
fit.mixed_1_nb <- glmer.nb(num_rest_in_chunk ~ avg_block_accuracy + cue_type + (1|subj_id),
                          data = model_data)
summary(fit.mixed_1_nb)

# Model 2: avg_block_accuracy is a sig neg predictor
fit.mixed_2_nb <- glmer.nb(num_rest_in_chunk ~ avg_block_accuracy + cue_type + gameA_isSR + (1|subj_id),
                          data = model_data)
summary(fit.mixed_2_nb)

# Model 3:avg_block_accuracy:cue_typeswitch is now significantly negative (when you do better and switch, you end up resting less than when you do worse and switch)
fit.mixed_3_nb <- glmer.nb(num_rest_in_chunk ~ avg_block_accuracy*cue_type + gameA_isSR + (1|subj_id),
                          data = model_data)
summary(fit.mixed_3_nb)

# Model 4: same as 3, also group_num is sig neg estimator (as time goes on you rest less)? maybe bc of costliness?
fit.mixed_4_nb <- glmer.nb(num_rest_in_chunk ~ group_num + avg_block_accuracy*cue_type + gameA_isSR + (1|subj_id),
                          data = model_data)
summary(fit.mixed_4_nb)

# Model 5: same as before but also spatial recall is a sig. neg predictor (if it was spatial recall you rest less)
fit.mixed_5_nb <- glmer.nb(num_rest_in_chunk ~ group_num + avg_block_accuracy*cue_type + gameA_isSR + game_type + (1|subj_id),
                          data = model_data)
summary(fit.mixed_5_nb)

# Compare models
compare_performance(fit.mixed_1_nb, fit.mixed_2_nb, fit.mixed_3_nb, fit.mixed_4_nb, fit.mixed_5_nb) # 5 is the best; r2 marg like 0.18

check_model(fit.mixed_5_nb)
summary(fit.mixed_5_nb) # 5 looks pretty good; better than poisson (improved overdispersion); later try to also include a preference variable (i.e. control for if participants pref sr or ds); and also try to include a variable for if they read the cues or not

fit.mixed_6_nb <- glmer.nb(num_rest_in_chunk ~ group_num + rest_type + avg_block_accuracy*cue_type + gameA_isSR + game_type + (1|subj_id),
                          data = model_data)
summary(fit.mixed_6_nb) # adding rest type didn't really make a big difference; worse model than 5

compare_performance(fit.mixed_5_nb, fit.mixed_6_nb)

best_model_q1q3 <- fit.mixed_5_nb


#######################################################
# extra just seeing impact of actually getting switched:
# 
# model_data_test_rest <- df_all_blockwise %>%
#   # Sort the data by subj_id and block_num to ensure correct order
#   arrange(subj_id, block_num) %>%
#   # Group by subject to ensure lag only looks at data within the same subject
#   group_by(subj_id) %>%
#   # Create the new columns using lag to get values from the previous row
#   mutate(
#     prev_switch_status = lag(cue_type),
#     prev_avg_block_accuracy = lag(avg_block_accuracy),
#     prev_num_rest = lag(num_rest_in_chunk)
#   ) %>%
#   # Remove the grouping
#   ungroup() %>%
#   filter(block_num != 1)
# 
# fit.testing_switch_on_next_rest_1 <- glmer.nb(num_rest_in_chunk ~ group_num + avg_block_accuracy*cue_type + gameA_isSR + game_type + prev_switch_status + (1|subj_id),
#                           data = model_data_test_rest)
# summary(fit.testing_switch_on_next_rest_1)
# 
# fit.testing_switch_on_next_rest_2 <- glmer.nb(num_rest_in_chunk ~ group_num + avg_block_accuracy*cue_type + gameA_isSR + game_type + prev_switch_status*prev_avg_block_accuracy + (1|subj_id),
#                           data = model_data_test_rest)
# summary(fit.testing_switch_on_next_rest_2)
# 
# fit.testing_switch_on_next_rest_3 <- glmer.nb(num_rest_in_chunk ~ group_num + avg_block_accuracy*cue_type + gameA_isSR + game_type + prev_switch_status*prev_avg_block_accuracy + prev_num_rest + (1|subj_id),
#                           data = model_data_test_rest)
# summary(fit.testing_switch_on_next_rest_3)

```

``` {r best_model_report}
report(fit.mixed_5_nb)

```
``` {r}
# USING THIS FOR CCN
ggplot(model_data, aes(x = avg_block_accuracy, 
                       y = num_rest_in_chunk,
                       color = cue_type)) +
  # Raw data points
  geom_point(alpha = 0.2, position = position_jitter(0.05, 0.05)) +
  # Use loess smoothing instead which is more flexible
  geom_smooth(method = "loess", span = 0.9,
              linewidth = 1.5) +
  # Labels and theme
  labs(x = "Average Epoch Accuracy", 
       y = "Subsequent Rest Duration",
       color = "Game Switch Type") +
  scale_color_manual(values = c("#0072B2", "#E99746"), 
                    labels = c("Told game would remain the same", "Told game would switch")) +
  ggtitle("Anticipating a task switch increases rest duration after low-efficacy epochs", 
          "Loess smoothed trend lines on raw participant data") +
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.title = element_text(face = "bold"),
        legend.title = element_text(face = "bold"),
        text = element_text(family = "Arial"),
        axis.title = element_text(face = "bold"))

# ggsave("task_switching_figure1.pdf", loess_plot_q3, width = 7, height = 5, dpi = 600)

#############################################################
# Create binned data with numeric bin centers
binned_data <- model_data %>%
  # Create bins and calculate bin centers
  mutate(accuracy_bin = cut(avg_block_accuracy, 
                          breaks = seq(0, 1, by = 0.25), 
                          include.lowest = TRUE),
         # Extract bin midpoints
         bin_center = 0.125 + 0.25 * (as.numeric(accuracy_bin) - 1)) %>%
  group_by(bin_center, cue_type) %>%
  summarize(mean_rest = mean(num_rest_in_chunk, na.rm = TRUE),
            se_rest = sd(num_rest_in_chunk, na.rm = TRUE)/sqrt(n()),
            n_obs = n(),
            .groups = "drop")

# Plot with bin centers instead of trying to convert factor to numeric
ggplot() +
  # Raw data points in background
  geom_point(data = model_data, 
             aes(x = avg_block_accuracy, y = num_rest_in_chunk, color = cue_type),
             alpha = 0.1, position = position_jitter(0.05, 0.05)) +
  # Binned averages
  geom_point(data = binned_data,
             aes(x = bin_center, y = mean_rest, color = cue_type),
             size = 3) +
  # Error bars 
  geom_errorbar(data = binned_data,
                aes(x = bin_center, 
                    ymin = mean_rest - se_rest, 
                    ymax = mean_rest + se_rest,
                    color = cue_type),
                width = 0.03) +
  # Connect points with lines
  geom_line(data = binned_data,
            aes(x = bin_center, y = mean_rest, color = cue_type, group = cue_type),
            linewidth = 1) +
  # Labels and theme
  labs(x = "Average Epoch Accuracy", 
       y = "Subsequent Rest Duration",
       color = "Game Switch Type") +
  scale_color_manual(values = c("#0097DF", "#E99746"), 
                    labels = c("Told game would remain the same", "Told game would switch")) +
  ggtitle("Anticipating a task switch increases rest duration after low-efficacy performance", 
          "Binned averages results") +
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.title = element_text(face = "bold"),
        legend.title = element_text(face = "bold"),
        axis.title = element_text(face = "bold"))


#### FINAL VERSION FOR CCN
ggplot(model_data, aes(x = avg_block_accuracy, 
                       y = num_rest_in_chunk,
                       color = cue_type)) +
  # Raw data points
  geom_point(alpha = 0.2, position = position_jitter(0.05, 0.05)) +
  # Use loess smoothing instead which is more flexible
  geom_smooth(method = "loess", span = 0.9,
              linewidth = 1.5) +
  # Labels and theme
  labs(x = "Average Epoch Accuracy", 
       y = "Subsequent Rest Duration",
       color = "Game Switch Type") +
  scale_color_manual(values = c("#0097DF", "#E99746"), 
                    labels = c("Told game would remain the same", "Told game would switch")) +
  ggtitle("Anticipating a task switch increases rest duration after low-efficacy epochs", 
          "Loess smoothed trend lines on raw participant data; Significant interaction effect in negative \nbinomial mixed-effects model.") +
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.title = element_text(size = 16),
        plot.subtitle = element_text(size = 12),
        legend.title = element_text(size = 14),
        legend.text = element_text(size = 12),
        text = element_text(family = "Arial", size = 12),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        panel.background = element_rect(fill = "white", color = NA),
        plot.background = element_rect(fill = "white", color = NA))

# # Save the plot to a PNG file with higher resolution
# ggsave("1a_big.png", width = 10, height = 8.5, dpi = 300)
```
``` {r}
# Create binned data for modeling (using categorical bins like the original)
model_data_binned <- model_data %>%
  mutate(acc_category = cut(avg_block_accuracy, 
                           breaks = c(-Inf, 0.25, 0.5, 0.75, Inf),
                           labels = c("Very Low", "Low", "Medium", "High"))) %>%
  filter(!is.na(acc_category), !is.na(num_rest_in_chunk))

# Fit mixed-effects model for rest duration but replace block accuracy with acc_category
# fit.model_5_nb 
mixed_model_rest <- glmer.nb(num_rest_in_chunk ~ group_num + acc_category*cue_type + gameA_isSR + game_type + (1|subj_id),
                          data = model_data_binned)

emm_rest <- emmeans(mixed_model_rest, ~ cue_type | acc_category)

# Get the pairwise comparisons within each accuracy category
simple_contrasts <- pairs(emm_rest)
print("Simple contrasts (effect of cue type within each accuracy category):")
print(simple_contrasts)

# test whether the switch-stay difference differs between accuracy categories
# create an object that represents the switch-stay difference at each accuracy level
switch_vs_stay <- list(diff = c(-1, 1))  # contrast coefficients for switch minus stay
diff_by_acc <- emmeans(mixed_model_rest, ~ cue_type | acc_category, contr = switch_vs_stay)
print("Switch minus Stay effect for each accuracy category:")
print(diff_by_acc$contrasts)

# Now test whether these differences differ between accuracy categories
# Compare each accuracy category to the others
interaction_contrasts <- pairs(diff_by_acc)
print("Interaction contrasts (comparing the switch effect between accuracy categories):")
print(interaction_contrasts)

# Visualize the interaction effect (the "difference of differences")
# Extract the switch-stay differences
diff_data <- as.data.frame(diff_by_acc$contrasts)
diff_data$acc_category <- as.factor(diff_data$acc_category)

# Plot the switch-stay difference by accuracy category
ggplot(diff_data, aes(x = acc_category, y = estimate)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = estimate - SE, ymax = estimate + SE), width = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "darkgray") +
  labs(x = "Average Epoch Accuracy",
       y = "Switch Effect (Switch - Stay)",
       title = "Difference in Rest Duration Between Switch and Stay Conditions",
       subtitle = "Positive values indicate longer rest after switch cues") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12, face = "bold"),
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 11)
  )
```

# JOINT PLOTS

Plot the best model's coefficients:
``` {r best_model_coeff_plot}
coef_data <- data.frame(
  term = names(fixef(fit.mixed_5_nb)),
  estimate = fixef(fit.mixed_5_nb),
  se = sqrt(diag(vcov(fit.mixed_5_nb)))
) %>%
  mutate(
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se,
    # Create readable labels
    term_clean = case_when(
      term == "(Intercept)" ~ "Intercept",
      term == "avg_block_accuracy" ~ "Avg Prior Block Accuracy",
      term == "gameA_isSRTRUE" ~ "Game A = SR",
      term == "game_typespatial_recall" ~ "Curr Game is SR",
      term == "cue_typeswitch" ~ "Cued to Switch",
      term == "avg_block_accuracy:cue_typeswitch" ~ "Prior Accuracy X Switch Cue",
      TRUE ~ term  # Keep original if no match
    ),
    # Add significance markers
    sig = case_when(
      abs(estimate) > 1.96 * se ~ "*",
      TRUE ~ ""
    )
  ) %>%
  # Reorder factors for better visualization
  mutate(term_clean = factor(term_clean, levels = rev(term_clean)))

# Create the enhanced plot
ggplot(coef_data, aes(x = estimate, y = term_clean)) +
  # Add shaded background for non-significant region
  geom_rect(aes(xmin = -1.96 * min(se), xmax = 1.96 * min(se), 
                ymin = -Inf, ymax = Inf),
            fill = "gray90", alpha = 0.5) +
  # Add vertical line at zero
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.8) +
  # Add error bars
  geom_errorbarh(aes(xmin = lower, xmax = upper), 
                height = 0.3, 
                color = "navy",
                linewidth = 1) +
  # Add points
  geom_point(size = 4, color = "navy", fill = "white", shape = 21) +
  # Add significance markers
  geom_text(aes(x = upper + 0.15, label = sig), 
            color = "navy", 
            size = 8) +
  # Customize labels and theme
  labs(x = "Coefficient Estimate",
       y = NULL,
       title = "Effect of Performance and Task Switching on Future Rest",
       subtitle = "Error bars show 95% confidence intervals\n* indicates significant effect") +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 14, color = "black"),
    axis.text.x = element_text(size = 14, color = "black"),
    axis.title.x = element_text(size = 14, face = "bold", margin = margin(t = 10)),
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12, color = "gray30"),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    plot.margin = margin(1, 1, 1, 1, "cm")
  ) +
  # Scale x axis to be symmetric and have nice breaks
  scale_x_continuous(
    limits = c(min(coef_data$lower) - 0.2, max(coef_data$upper) + 0.2),
    breaks = scales::pretty_breaks(n = 6)
  )

#################################
### PLOT IT IN BETTER WAY
best_model_q1_q3 <- fit.mixed_5_nb
  
coef_data <- tidy(best_model_q1_q3, effects = "fixed",conf.int = TRUE) 
coef_data <- coef_data %>%
  mutate(
    term = case_when(
      term == "(Intercept)" ~ "Intercept",
      term == "avg_block_accuracy" ~ "Avg Prior Block Accuracy",
      term == "gameA_isSRTRUE" ~ "Game A = Spatial Recall condition",
      term == "game_typespatial_recall" ~ "Previous Block = Spatial Recall",
      term == "cue_typeswitch" ~ "Cued That Game Will Switch After This Rest Period",
      term == "avg_block_accuracy:cue_typeswitch" ~ "Prior Accuracy X Switch Cue",
      term == "group_num" ~ "Block Number in Experiment",
      TRUE ~ term  # Keep original if no match
    )
  )
# More publication-ready plot
ggplot(coef_data, aes(y = reorder(term, estimate), x = estimate)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_pointrange(aes(xmin = conf.low, xmax = conf.high, color = p.value < 0.05)) +
    scale_color_manual(values = c("TRUE" = "black", "FALSE" = "gray60"), 
                      labels = c("p ≥ 0.05", "p < 0.05"),
                      name = "Significance") +
    labs(x = "Coefficient Estimate", y = NULL,
         title = "Fixed Effects Coefficients of Model Predicting Rest Period Length",
         subtitle = "With 95% Confidence Intervals") +
    theme_minimal() +
    theme(legend.position = "bottom",
          axis.text.y = element_text(size = 11),
          panel.grid.minor = element_blank())

```

Plot the best model's predictions:
``` {r best_model_pred}
# Get predicted effects
pred_effects_5_nb <- as.data.frame(effect("avg_block_accuracy:cue_type", fit.mixed_5_nb))

# plot best model predictions by cue type in one graph: 
ggplot(data = pred_effects_5_nb, aes(x = avg_block_accuracy, y = fit, color = cue_type, fill = cue_type)) +
  geom_line(size=1.5) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.05) +
  geom_point(data = model_data, aes(x = avg_block_accuracy, y = num_rest_in_chunk), 
             alpha = 0.2, position = position_jitter(0.01,0.01)) +
  theme_minimal() +
  labs(x = "Block Accuracy", 
       y = "Predicted Number of Rests",
       color = "Cue Type",
       fill = "Cue Type") +
  guides(fill = "none") 

# plot best model predictions by cue type in a faceted graph
ggplot(data = pred_effects_5_nb, aes(x = avg_block_accuracy, y = fit)) +
  facet_wrap(~cue_type) +
  geom_line(size = 1.5) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.1, fill = "grey") +
  geom_point(data = model_data, aes(x = avg_block_accuracy, y = num_rest_in_chunk), 
             alpha = 0.2, position = position_jitter(0.01,0.01)) +
  theme_minimal()
``` 

Plot the best model's predictions and raw data side by side:
``` {r best_model_pred}
# Get predicted effects
pred_effects_5_nb <- as.data.frame(effect("avg_block_accuracy:cue_type", fit.mixed_5_nb))

# Extract model summary
model_summary <- summary(fit.mixed_5_nb)
coef_table <- model_summary$coefficients

# Extract specific coefficients and p-values
acc_beta <- round(coef_table["avg_block_accuracy", "Estimate"], 3)
acc_p <- round(coef_table["avg_block_accuracy", "Pr(>|z|)"], 3)
int_beta <- round(coef_table["avg_block_accuracy:cue_typeswitch", "Estimate"], 3)
int_p <- round(coef_table["avg_block_accuracy:cue_typeswitch", "Pr(>|z|)"], 3)

# Create label text programmatically
label_text <- sprintf("Accuracy: β = %0.3f, p = %0.3f\nAccuracy:Cue_type: β = %0.3f, p = %0.3f",
                     acc_beta, acc_p, int_beta, int_p)

# Define consistent colors
color_scale <- c("stay" = "salmon", "switch" = "turquoise3")

# FOR RAW DATA SEE IF THE LINES ARE SIGNIFICANLY DIFFERENT:
# Test for difference in slopes
raw_data_model <- lm(num_rest_in_chunk ~ avg_block_accuracy * cue_type, data = model_data)
summary(raw_data_model)
# Get model results
model_sum <- summary(raw_data_model)
int_p <- round(coef(model_sum)["avg_block_accuracy:cue_typeswitch", "Pr(>|t|)"], 3)
int_b <- round(coef(model_sum)["avg_block_accuracy:cue_typeswitch", "Estimate"], 3)


# Model predictions plot
p1 <- ggplot(data = pred_effects_5_nb, aes(x = avg_block_accuracy, y = fit)) +
  geom_line(aes(color = cue_type, key = cue_type), size = 1) +  # add key aesthetic
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = cue_type), alpha = 0.1) +
  geom_point(data = model_data, aes(x = avg_block_accuracy, y = num_rest_in_chunk, color = cue_type), 
             alpha = 0.2, position = position_jitter(0.01,0.01)) +
  theme_minimal() +
  labs(x = "Block Accuracy", 
       y = "Predicted Number of Rests",
       title = "Model Prediction") +
  scale_color_manual(name = "Cue Type", values = color_scale) +
  scale_fill_manual(name = "Cue Type", values = color_scale) +
  guides(fill = "none") +
  annotate("text", x = 0.1, y = 15, 
           label = label_text,
           hjust = 0, size = 3)

# Raw data plot
# Add to plot p2
p2 <- ggplot(data = model_data, aes(x = avg_block_accuracy, y = num_rest_in_chunk)) +
  geom_point(aes(color = cue_type), alpha = 0.2, position = position_jitter(0.01,0.01)) +
  geom_smooth(aes(color = cue_type), method = "lm", size = 1, alpha = 0.05) +
  theme_minimal() +
  labs(x = "Block Accuracy", 
       y = "Number of Rests",
       title = "Raw Data Trends") +
  scale_color_manual(values = color_scale) +
  annotate("text", x = 0.1, y = 15,
           label = sprintf("Slope difference: β = %.3f, p = %.3f", int_b, int_p),
           hjust = 0, size = 3)

# Wrap both plots with a consistent guide
(p1 + p2) &
  guides(color = guide_legend(override.aes = list(size = 1))) &
  theme(legend.position = "right")


p1
p2
```

Plot the raw data in bar graph form:
``` {r raw_data_cue_rest_bar_graph}
# plot the raw data to look at avg block accuracy, following rest num, and cue type
# Create binned version
model_data$acc_bin <- cut(model_data$avg_block_accuracy, 
                         breaks = seq(0, 1, by = 0.25),
                         labels = c("0-0.25", "0.25-0.5", "0.5-0.75", "0.75-1"),
                         include.lowest=TRUE)


# basic plot with no significnace tests
# Create summary plot with means and standard errors
ggplot(model_data, aes(x = acc_bin, y = num_rest_in_chunk, fill = cue_type)) +
  stat_summary(fun = mean, geom = "bar", position = position_dodge()) +
  stat_summary(fun.data = mean_se, geom = "errorbar", position = position_dodge(width = 0.9), width = 0.2) +
  theme_minimal() +
  labs(x = "Prior Average Block Accuracy", 
       y = "Average Number of Rests",
       fill = "Cue Type") +
  scale_fill_manual(values = c("salmon", "turquoise3")) +
  ggtitle("Average number of rests following binned block accuracy levels, by cue type","raw data: not accounting for subject variability or other effects")


# add significance testing
ggplot(model_data, aes(x = acc_bin, y = num_rest_in_chunk, fill = cue_type)) +
  stat_summary(fun = mean, geom = "bar", position = position_dodge()) +
  stat_summary(fun.data = mean_se, geom = "errorbar", position = position_dodge(width = 0.9), width = 0.2) +
  theme_minimal() +
  labs(x = "Prior Average Block Accuracy", 
       y = "Average Number of Rests",
       fill = "Cue Type") +
  scale_fill_manual(values = c("salmon", "turquoise3")) +
  ggtitle("Average number of rests following binned block accuracy levels, by cue type",
          "raw data: not accounting for subject variability or other effects") +
  stat_compare_means(aes(group = cue_type), 
                    method = "t.test",
                    label = "p.signif",
                    label.y = 15)


ggplot(model_data, mapping = aes(x=cue_type, y=num_rest_in_chunk, fill=cue_type)) +
  stat_summary(fun = mean, geom = "bar", position = position_dodge()) +
  stat_summary(fun.data = mean_se, geom = "errorbar", position = position_dodge(width = 0.9), width = 0.2) +
  theme_minimal() +
  labs(x = "Cue Type", 
       y = "Average Number of Rests",
       fill = "Cue Type") +
    scale_fill_manual(values = c("salmon", "turquoise3")) +
  stat_compare_means(aes(group = cue_type), 
                    method = "t.test",
                    label = "p.signif",
                    label.y = 15)

```


# Q1 SPECIFIC PLOTS
``` {r rest_acc_plot}
lm_model <- df_all_blockwise %>%
  ungroup() %>%
  lm(num_rest_in_chunk ~ avg_block_accuracy, data = .)

# Get R-squared value
r_squared <- summary(lm_model)$r.squared
r_squared_label <- sprintf("R² = %.3f", r_squared)
p_value <- anova(lm_model)$"Pr(>F)"[1]

# Calculate Cohen's f² effect size
# f² = R² / (1 - R²)
f_squared <- r_squared / (1 - r_squared)

# For simple regression, we can convert r to d
# First get r (correlation)
r <- sqrt(r_squared) * sign(coef(lm_model)[2])  # multiply by sign of slope
# Convert r to d using the formula: d = 2r/sqrt(1-r^2)
cohens_d <- (2 * r) / sqrt(1 - r^2)

# Create formatted labels
stats_label <- sprintf("R² = %.3f\nf² = %.3f\nd = %.3f\np = %.3e", 
                      r_squared, f_squared, cohens_d, p_value)
df_all_blockwise %>%
  ggplot(mapping = aes(x = avg_block_accuracy, y = num_rest_in_chunk)) +
  geom_smooth(method="lm", se=TRUE) +
  geom_point(mapping = aes(color = block_num), size = 0.5, position = position_jitter(0.05,0.05)) +
  scale_x_reverse() +  # Flip x-axis
  annotate("text", 
           x = 0.5,  
           y = 15,
           label = stats_label,
           size = 3) +  # Larger text
  labs(x = "Average block accuracy",
       y = "Following rests taken",
       color = "Block Number") +
  ggtitle("Predicting rest from performance (fixed effects only)") +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    plot.title = element_text(size = 16),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )


df_all_blockwise %>%
  ggplot(mapping = aes(x = avg_block_accuracy, y = num_rest_in_chunk)) +
  geom_smooth(method="lm", se=TRUE) +
  geom_point(mapping = aes(color = block_num), size = 0.5, position = position_jitter(0.05,0.05)) +
  # scale_x_reverse() +  # Flip x-axis
  annotate("text", 
           x = 0.5,  
           y = 15,
           label = stats_label,
           size = 3) +  # Larger text
  labs(x = "Average block accuracy",
       y = "Following Rest Trials Taken",
       color = "Block Number") +
  ggtitle("Predicting rest from performance (fixed effects only)") +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    plot.title = element_text(size = 16),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )


df_all_blockwise %>%
  ggplot(mapping = aes(x = avg_block_accuracy, y = num_rest_in_chunk)) +
  geom_smooth(method="lm", se=TRUE) +
  geom_point(size = 0.5, position = position_jitter(0.05,0.05)) +
  # scale_x_reverse() +  # Flip x-axis
  annotate("text", 
           x = 0.5,  
           y = 15,
           label = stats_label,
           size = 3) +  # Larger text
  labs(x = "Average block accuracy",
       y = "Following Rest Trials Taken",
       color = "Epoch Number") +
  ggtitle("Lower efficacy epochs are associated with longer rests", "Fixed effects plot; same relationship trend found in logistic mixed effects model") +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    plot.title = element_text(size = 16)
  )
```

# Q3 SPECIFIC PLOTS

``` {r rest_acc_plot}
# look at switch vs stay overall
breaks <- c(-Inf, -1, 0, 1, Inf)
labels <- c('prev acc << avg','prev acc < avg', 'prev acc > avg', 'prev acc >> avg')

temp <- df_all_blockwise %>%
  group_by(subj_id) %>%
  mutate(accuracy_bin_preceding = cut(scale_accuracy, breaks = breaks, labels = labels, right = FALSE)) %>%
  ungroup() %>%
  filter(!is.na(scale_accuracy))

temp <- temp %>%
  select(subj_id, cue_type, num_rest_in_chunk, accuracy_bin_preceding)

temp %>%
  ggplot(mapping = aes(x=cue_type, y=num_rest_in_chunk)) +
  facet_wrap(~accuracy_bin_preceding, ncol=4) +
  theme_bw() +
  theme(
    panel.spacing.x = unit(2, "lines"),
    strip.text = element_text(size = 13),
    axis.title = element_text(size = 13),
    axis.text = element_text(size = 12)
  ) +
  geom_point(alpha=0.15, position = position_jitter(width=0.3, height=0), size = 0.4) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "light blue",
               shape = 21,
               size = 0.75) +
  labs(x = "What did the cue say?",
       y = "Rest amount following this cue") +
  ggtitle("Relationship between prior block performance, switch status, and rest time")






temp <- df_all_blockwise %>%
  group_by(subj_id) %>%
  mutate(accuracy_bin_preceding = cut(scale_accuracy, breaks = breaks, labels = labels, right = FALSE)) %>%
  ungroup() %>%
  filter(!is.na(scale_accuracy), !is.na(scale_rest))

temp <- temp %>%
  select(subj_id, cue_type, scale_rest, accuracy_bin_preceding)

temp %>%
  ggplot(mapping = aes(x=cue_type, y=scale_rest)) +
  facet_wrap(~accuracy_bin_preceding, ncol=4) +
  theme_bw() +
  theme(
    panel.spacing.x = unit(2, "lines"),
    strip.text = element_text(size = 13),
    axis.title = element_text(size = 13),
    axis.text = element_text(size = 12)
  ) +
  geom_point(alpha=0.15, position = position_jitter(width=0.3, height=0), size = 0.4) +
  stat_summary(fun.data = "mean_cl_boot",
               geom = "pointrange",
               color = "black",
               fill = "light blue",
               shape = 21,
               size = 0.75) +
  labs(x = "What did the cue say?",
       y = "Scale rest amount following this cue") +
  ggtitle("Relationship between prior block performance, switch status, and rest time")
```



# more model tests (use the report package to investigate the current best model, but also test to see if adding in other vars makes model better)
Things to add:
- plot how it changes over time
- add a game type preference variable?
- add a cue read variable? / look only at people who explicitly said they read the cue


